---
title: "FIFAAnalysis"
author: "Ishaan Advani"
date: "19 December 2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is my Analysis MarkDown file. I will address the questions I mentioned in the readme file. 

I will first create a GroupObject
```{r cars}
minimum_ovr <- 70
maximum_ovr <- 80
minimum_age <- 20
maximum_age <- 30
source("FIFAConfig.R")
data <- load_filtered_dataset()
GObj1 <- GroupObj(minimum_ovr, maximum_ovr, minimum_age, maximum_age, data)
```

Now that my Group Object has been created I will try and create an overvalued object that will help in identifying which players are valued at a premium.

```{r pressure, echo=FALSE}
OvObj1 <- Salary_Ovr(GObj1)
```


Now I will analyse 3 traits for the players valued at a premium and identify the relationship the traits have to the premium ratio. I will do this using regression and ggplot.
```{r pressure1, echo=FALSE}
traitlist <- c("Passing", "Pace", "Physical")
ValuableTraits(OvObj1, traitlist)
```

Now I will analyse 3 traits for the players valued at a premium and identify the relationship the traits have to the premium ratio. I will do this using regression and ggplot.
```{r pressure2, echo=FALSE}
traitlist <- c("Passing", "Pace", "Physical")
ValuableTraits(OvObj1, traitlist)
```

I will now move on to analysis from the perspective of different countries/leagues. Each country has a typical playing style that requires more of some attributes and less of other. For example, players in Spain tend to have higher passing abilities than physical abilities in general. I will first create a country object based on a list of countries/leagues I extracted from the group object.
```{r pressure3, echo=FALSE}
countrylist <- get_league.Group(GObj1)
for (i in 1:7)
{
print(paste0("The country I'm going to be analysing is ", countrylist[i]))
countobj <- CountryObj(countrylist[i], data)
traitlist <- c("Passing", "Pace", "Physical")
CountryTraits(countobj, traitlist)
}
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
