---
title: "ReadMeFIFA"
author: "Ishaan Advani"
date: "19 December 2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is my R Markdown Readme.

The dataset I've used is FIFA 18 Player Stats that I obtained from Kaggle. The dataset contains information like speed, value, wages and physical abilities for all the players in the game.

I will perform the following tasks and answer the following questions in my analysis-
Creating a Group object  - I will restrict my analysis to specific age and overall rating ranges. Players are sometimes valued unfairly after a specific overall rating value.

Creating an Over Valued object - Subsegmenting players who are perhaps valued excessively highly in comparison to the maximum rating they can achieve.

How do some major traits link to how much a club is willing to pay the player?

Creating an Country object (Salary_Ovr) - Subsegmenting players who play in the same league/country. 

How do countries value some of the major skills of a player differently?

How does a players overall rating relate to his major skills?

```{r cars}
source("FIFAConfig.R")
```
